19Q2

### 2019-07-22 19Q2.Rmd
work on coding lineage mut heatmaps

crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
# write.csv.gz(crispr %>% drop_na(Score), "./../htscreens_giant_files/crispr_data_19Q2.csv.gz")
```

```{r read_crispr_data}
crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds")
```

@@

@@

ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
ccle_signif_g2p_dg <- merge(ccle_signif_g2p_dg, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")
ccle_signif_dgl <- merge(ccle_signif_dgl, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)

ctrp_signif_g2p_dg <- readRDS("./data_munging/rds/ctrp_signif_g2p_dg.rds")
ctrp_signif_g2p_dg <- merge(ctrp_signif_g2p_dg, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")
ctrp_signif_dgl <- merge(ctrp_signif_dgl, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)

gdsc_signif_g2p_dg <- readRDS("./data_munging/rds/gdsc_signif_g2p_dg.rds")
gdsc_signif_g2p_dg <- merge(gdsc_signif_g2p_dg, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
gdsc_signif_dgl <- merge(gdsc_signif_dgl, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
```

@@

lins <- union(unique(ccle_signif_dgl$disease), union(unique(ctrp_signif_dgl$disease), unique(gdsc_signif_dgl$disease)))

drug_gene_lins <- unique(rbind(select(ccle_signif_dgl, Gene, Drug, disease, Direction_Curated), select(ctrp_signif_dgl, Gene, Drug, disease, Direction_Curated), select(gdsc_signif_dgl, Gene, Drug, disease, Direction_Curated)))

ccle_signif_prot_4plot <- merge(merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)

ctrp_signif_prot_4plot <- merge(merge(merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
gdsc_signif_prot_4plot <- merge(merge(merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
```

@@

```{r}
MakeWilcoxonLineageHeatmap <- function(all_lin_df, lineage) {
  use_data <- filter(all_lin_df, Gene %in% unique(g2p_mut$Gene) & disease == lineage)
  ccle_df <- filter(use_data, Database == "CCLE")
  ctrp_df <- filter(use_data, Database == "CTRP")
  gdsc_df <- filter(use_datas, Database == "GDSC")

@@

  ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_df, feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 6, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)

  ht <- ht_ccle + ht_ctrp + ht_gdsc
  return(ht)
}
```

```
lin_ht <- lapply(lineages, makeDrugBoxplots, dataset = "CCLE")
ccle_lvlA_drugboxplot_paths <- paste0(ccle_drugs, "_ccle_boxplots.png")
pwalk(list(ccle_lvlA_drugboxplot_paths, ccle_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_lvlA_boxplots", dpi = 450, width = 12, height = 7, units = "in")

 draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
```

>>>>

crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/crispr_data_19Q2.rds")
# write.csv.gz(crispr %>% drop_na(Score), "./../htscreens_giant_files/crispr_data_19Q2.csv.gz")
```

```{r read_crispr_data}
crispr <- readRDS("./../htscreens_giant_files/crispr_data_19Q2.rds")
```

@@

g2p_mut_summ_lin <- g2p_mut %>% count(Drug, Gene, disease, Direction_Curated) %>% select(-n)
g2p_mut_summ_lin_n <- g2p_mut_summ_lin %>% count(Drug, Gene, disease)
g2p_mut_summ_lin <- merge(g2p_mut_summ_lin, g2p_mut_summ_lin_n, by = c("Drug", "Gene", "disease"))
g2p_mut_summ_lin$Direction_Heatmap <- with(g2p_mut_summ_lin, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
g2p_mut_summ_lin <- unique(select(g2p_mut_summ_lin, Drug, Gene, disease, Direction_Heatmap))

@@

ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
ccle_signif_g2p_dg <- merge(ccle_signif_g2p_dg, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")
ccle_signif_dgl <- merge(ccle_signif_dgl, g2p_mut_summ_lin, by = c("Drug", "Gene", "disease"), all.x = TRUE)

ctrp_signif_g2p_dg <- readRDS("./data_munging/rds/ctrp_signif_g2p_dg.rds")
ctrp_signif_g2p_dg <- merge(ctrp_signif_g2p_dg, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")
ctrp_signif_dgl <- merge(ctrp_signif_dgl, g2p_mut_summ_lin, by = c("Drug", "Gene", "disease"), all.x = TRUE)

gdsc_signif_g2p_dg <- readRDS("./data_munging/rds/gdsc_signif_g2p_dg.rds")
gdsc_signif_g2p_dg <- merge(gdsc_signif_g2p_dg, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
gdsc_signif_dgl <- merge(gdsc_signif_dgl, g2p_mut_summ_lin, by = c("Drug", "Gene", "disease"), all.x = TRUE)
```

### Lineages

@@

genes <- union(unique(ccle_signif_dgl$Gene), union(unique(ctrp_signif_dgl$Gene), unique(gdsc_signif_dgl$Gene)))
diseases <- union(unique(ccle_signif_dgl$disease), union(unique(ctrp_signif_dgl$disease), unique(gdsc_signif_dgl$disease)))

ccle_signif_dgl_4plot <- merge(merge(ccle_signif_dgl, unique(select(ccle_filt, Drug, Gene, disease)), by = c("Drug", "Gene", "disease"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_dgl$Drug), "Gene" = genes, "disease" = diseases), by = c("Drug", "Gene", "disease"), all = TRUE)
ccle_signif_dgl_4plot$Database <- "CCLE"

ctrp_signif_dgl_4plot <- merge(merge(ctrp_signif_dgl, unique(select(ctrp_filt, Drug, Gene, disease)), by = c("Drug", "Gene", "disease"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_dgl$Drug), "Gene" = genes, "disease" = diseases), by = c("Drug", "Gene", "disease"), all = TRUE)
ctrp_signif_dgl_4plot$Database <- "CTRP"

gdsc_signif_dgl_4plot <- merge(merge(gdsc_signif_dgl, unique(select(gdsc_filt, Drug, Gene, disease)), by = c("Drug", "Gene", "disease"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_dgl$Drug), "Gene" = genes, "disease" = diseases), by = c("Drug", "Gene", "disease"), all = TRUE)
gdsc_signif_dgl_4plot$Database <- "GDSC"
```

@@

```{r}
MakeWilcoxonLineageHeatmap <- function(all_lin_df, lineage) {
  use_data <- filter(all_lin_df, Gene %in% unique(g2p_mut$Gene) & disease == lineage)
  ccle_df <- filter(use_data, Database == "CCLE")
  ctrp_df <- filter(use_data, Database == "CTRP")
  gdsc_df <- filter(use_data, Database == "GDSC")

@@

  ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_df, feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)

  ht <- ht_ccle + ht_ctrp + ht_gdsc
  return(ht)
}

SaveWilcoxonLineageHeatmap <- function(ht, outfile) {
  png(filename = outfile, width = 13, height = 9.5, units = "in", res = 500)
  draw(ht, gap = unit(0.25, "in"), heatmap_legend_side = "top")
  dev.off()
}
```

```{r, eval=FALSE}
diseases <- union(unique(ccle_signif_dgl_4plot$disease), union(unique(ctrp_signif_dgl_4plot$disease), unique(gdsc_signif_dgl_4plot$disease)))

drugscreens_all_signif_mut <- rbind(ccle_signif_dgl_4plot, ctrp_signif_dgl_4plot, gdsc_signif_dgl_4plot)

lin_hts <- lapply(diseases, MakeWilcoxonLineageHeatmap, all_lin_df = drugscreens_all_signif_mut)
lin_ht_paths <- paste0(lins, "_mut_heatmap.png")
pwalk(list(lin_ht_paths, lin_hts), SaveWilcoxonLineageHeatmap, outfile = "./plots/manuscript/lineage_heatmaps")
```
